\begin{minipage}[t]{0.9\textwidth}
	\subsection*{\textcolor{colorTitelErfarenhet}{CGI, Server Manager Client – 2023/08 to 2023/09}}
	Björn was the sole developer for this project, managing various functions of a server ranging from service monitoring to a file retrieval interface. The user interface uses scalable vector graphics to achieve better user-friendliness and aesthetics. Development was implemented following all the steps in a CI/CD process.
	
	\vspace{5pt}\textit{Technologies used: Node.js, TypeScript, JavaScript, Vue3, HTML, CSS, GIT, Bash, Linux, and SVG.}
	
	\vspace{15pt} % Adjust vertical placement of minipage
	
\subsection*{\textcolor{colorTitelErfarenhet}{CGI, Blekingetrafiken Bus App – 2023/08 to 2023/08}}
Björn was the sole developer where he performed all steps in the process from CI/CD, implementation, testing, to project publication. The project helps Björn and others to check transportation to and from the CGI office for more efficient time management. The app uses Blekingetrafiken's API to retrieve data on various destinations.

\vspace{5pt}\textit{Technologies used: Python3, GIT, Bash, Linux, Docker, and Jenkins.}

\vspace{15pt} % Adjust vertical placement of minipage

\subsection*{\textcolor{colorTitelErfarenhet}{CGI, Flexmeister – 2023/06 to 2023/08}}
To more efficiently log and manage employees' flex time, Björn was involved in creating a flex time management app with a web-based client and a server with a Rest API designed to be extensible if more types of clients were needed. Development was implemented following all the steps in a CI/CD process.

\vspace{5pt}\textit{Technologies used: Python3, GIT, Bash, Linux, Docker, and Jenkins.}

\vspace{15pt} % Adjust vertical placement of minipage
\subsection*{\textcolor{colorTitelErfarenhet}{CGI, Student Project in collaboration with BTH, Software Developer - 2020/02 to 2020/06}}
Together with his team, Björn developed a drawing management system for the navy. The project used agile workflows with the use of the Jira tool. Development included Java, Spring Boot, Unit Testing, and Integration tests.

\vspace{5pt}\textit{Technologies used: Java, JavaScript, Spring Boot, Visual Studio Code, Gradle, Git, Jira, Unit Testing, and Integration tests.} 

\vspace{15pt} % Adjust vertical placement of minipage
\subsection*{\textcolor{colorTitelErfarenhet}{SIGMA, Web/Software Development - 2019/02 to 2019/07}}
During this time, Björn, along with his team, developed a transportation system for Karlskrona municipality, which is now used by municipal employees to book transportation. He was a full-stack developer focusing on testing and front-end development.

\vspace{5pt}\textit{Technologies used: JavaScript, Dart, NodeJs, Gradle, MariaDB, Azure, Google Cloud, Git, React.js, and Maven, Docker.} 

\vspace{15pt} % Adjust vertical placement of minipage

\subsection*{\textcolor{colorTitelErfarenhet}{Sjobeck Prime, Server Manager/Software Development - 2014/01 to 2014/08}}
During his time at Sjobeck Prime, Björn set up Linux-based development servers and developed prototypes for iPhone. He was also responsible for internal servers and services.

\vspace{5pt}\textit{Technologies used: Java, Bash, Objekt-C, MySQL, XCode, Linux, Git, and Jira} 

\vspace{15pt} % Adjust vertical placement of minipage
\subsection*{\textcolor{colorTitelErfarenhet}{Simrishamn Municipality, IT Department - 2011/03 to 2011/09}}
Björn developed the municipality's reporting system for home care, mostly in the .NET programming language.

\vspace{5pt}\textit{Technologies used: MySQL, .NET, JavaScript, Visual Studio, and Git.}


\vspace{15pt} % Adjust vertical placement of minipage
\subsection*{\textcolor{colorTitelErfarenhet}{Crunch Fish, APU/ Android app development - 2009/01 to 2010/01}}
Björn worked on developing a music-focused app for Android. He also contributed to prototyping for future projects.

\vspace{5pt}\textit{Technologies used: Java, XML, HTML, and Android Studio.}
\end{minipage}%